Need a good title.

### 2017-11-13 ms.tex
temp push

\usepackage{alltt}
\usepackage[sort]{natbib}
\usepackage{amsmath}
\usepackage{alltt}
\usepackage{hyperref}
\usepackage[utf8]{inputenc} % for accented characters
%% stuff for editing
%\usepackage[markup=nocolor,addedmarkup=bf,deletedmarkup=sout]{changes}
%% to suppress notes & comments: \usepackage[final]{changes}
\usepackage[backgroundcolor=lightgray]{todonotes}
\usepackage{setspace}
\bibliographystyle{chicago}
\title{Fitting phylogenetic generalized linear mixed models}
\author{Michael Li and Ben Bolker}
\date{\today}

@@

%For example, regression analyses of body temperature as a function of body size for animal within a clade, species compositions in different sites, etc. 
The most widely used statistical method to model/fit related species data that accounts for phylogenetic structure is the phylogenetic regression (Felsenstein 1985). 
More recently, researchers use (turn to?) linear mixed model and generalized linear mixed model framework to model complex systems with phylogenetic structures. 
\ml{Why? Data type, interactions, random effects, etc... Need to really explain random effects here.}
Despite the choice of modeling strageties, there isn't a convient platform to do all and limited in model complexities additional complexities in the systems.

In this paper, we model it using lme4 and test it with simulated cases and fit it to dun (maybe more examples if we can find it) example. 
We also compare different platforms.

>>>>

\usepackage{alltt}
\usepackage[sort]{natbib}
\usepackage{amsmath}
\usepackage{alltt}
\usepackage{hyperref}
\usepackage[utf8]{inputenc} % for accented characters
%% stuff for editing
%\usepackage[markup=nocolor,addedmarkup=bf,deletedmarkup=sout]{changes}
%% to suppress notes & comments: \usepackage[final]{changes}
\usepackage[backgroundcolor=lightgray]{todonotes}
\usepackage{setspace}
\bibliographystyle{chicago}
\title{Need a good title.}
\author{Michael Li and Ben Bolker}
\date{\today}

@@

%For example, regression analyses of body temperature as a function of body size for animal within a clade, species compositions in different sites, etc. 
The most widely used statistical method to model/fit related species data that accounts for phylogenetic structure is the phylogenetic regression (Felsenstein 1985).
The typical phylogenetic regression is of the form:
\begin{align}
y & = XB + \epsilon \\
\epsilon & \sim MVN(0,\sigma^{2}C),
\end{align}
where $y$ is an $n \times 1$ vector of measureable response phenotypic trait; $X$ is an $n \times (m + 1)$ model matrix containing 1's in the first column and the $m$ independment variable (traits); $B$ is an $m \times 1$ coefficient vector; $\espilon$ is the residual error and assumed to be multivariate normally distributed with a variance-covariance matrix given by $\sigma^{2}_{ \epsilon} C$ in which $C$ is the phylogenetic correlation (PC).
\ml{Need to say something like $\epsilon$ explains all the phylogenetic corelation and error or zero residual}

More recently, researchers use linear mixed model and generalized linear mixed model framework to model complex systems with phylogenetic structures.
\ml{Why? Data type, interactions, random effects, etc... Need to really explain random effects here. Alternatively, we can drop this line and write this...}
An alternative modelling approach is to use linear mixed effects modelling framework.
The typical phylogenetic linear mixed model has the form:
\begin{align}
Y & \sim N(XB + Zb, \sigma^{2}),
\end{align}
Despite the choice of modeling strageties, there isn't a convient platform to do all and limited in model complexities additional complexities in the systems and . 
\ml{This sounds cheesy}

In this paper, we took a simple, yet effective alternative approach model to model phylogenetic correlation where we ... . We used lme4 and test it with simulated cases and fit it to dun (maybe more examples if we can find it) example. 
We will compare our simulations and example fits to different platforms.
